The first high-redshift Changing Look Quasars

### 2019-11-07 tex/other_tex/201910/CIV_CLQs_20191016.tex
CIV tex/ tidy up

\hypersetup{draft}
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

@@

\subsection{Line Properties}  
We use the measured quasar emission line properties from
\citet{Shen2011} and \citet{Hamann2017}. \citet{Hamann2017} in
particular investigate in robust detail the UV continuum and the \civ\
(and \nv $\lambda$ $\lambda$1238, 1242) emission lines in over 200,000
quasars in BOSS DR12Q \citep{Paris2017}\footnote{This emission-line
catalog can be downloaded from
\href{https://datadryad.org/stash/dataset/doi:10.6086/D1H59V}{here}.}
The quasar redshift are limited to the range $1.53 \leq z \leq 5.0$ so
that \civ\ and the adjacent continuum are covered by BOSS. These
measurements provide line profile information and N V/C IV flux
ratios.

@@

  \begin{tabu}{lll  cccc r }

@@

    Object                               &   MJD       & line              & Line  Lumin.          &  FWHM                      &  $V_{\rm off}$          & E.W.                          &     Catalog  \\                                   

@@

    \rowfont{\color{blue}}       & 53948     &  \civ             &   570$\pm$14      &   9003$\pm$261      &  1487$\pm$76      &  18.09$\pm$0.46         &      \\
    \rowfont{\color{blue}}       & 53948     &   \civ            &    ---                   &    5230$\pm$736      &    ---                     &    30.1$\pm$1.21        &  Shen2011  \\
    \rowfont{\color{blue}}        & 53948    &   \civ            &  1254                   &    5119$^{(a)}$          &    ---                     &   ---                            &  SDSS DR12 SAS  \\
                                              & 53948     &  \ciii            &   467$\pm$15     &  13707$\pm$491      &  2983$\pm$223    &  25.90$\pm$0.84         &     \\
                                              &  53948    &  \ciii            &   449                    &     5119$^{(a)}$          &  ---                        &    ---                           &  SDSS DR12 SAS \\
  \rowfont{\color{teal}}         & 53948     &  \mgii         &   209$\pm$7       &     5063$\pm$175     &  $-227\pm77$         &  21.43$\pm$0.69       &     \\
  \rowfont{\color{teal}}         & 53948     &  \mgii         &   ---                    &     4730$\pm$313     &  ---                         &  32$\pm$3.88            &    Shen2011 \\

@@

                &     \textcolor{teal}{53948}      & \textcolor{teal}{\mgii}   & \textcolor{teal}{405} & \textcolor{teal}{5119$^{(a)}$}   &  \textcolor{teal}{---}   & \textcolor{teal}{---}        &   \textcolor{teal}{SDSS DR12 SAS}    \\

@@

    \rowfont{\color{blue}}        & 58538      &  \civ             &    90$\pm$2        &   13112$\pm$208          &  1333$\pm$69      &   45.44$\pm$0.86     &     \\  
                                              & 58538      &  \ciii              &    83$\pm$1       &   14913$\pm$245          &    942$\pm$93      &   52.99$\pm$0.91     &     \\  
    \rowfont{\color{teal}}         & 58538      &  \mgii           &     71$\pm$2      &   14951$\pm$340          &    -63$\pm$129    &   77.08$\pm$1.69    &     \\

@@

    \rowfont{\color{blue}}        & 58693          &  \civ          &  1006$\pm$1     &   13685$\pm$127          &   3000                     &   17.19$\pm$0.17    &     \\  
                                              & 58693          &  \ciii           &    151$\pm$1     &   15000                          &   3000                      &    39.31$\pm$0.24    &     \\  
    \rowfont{\color{teal}}         & 58693           &  \mgii       &    180$\pm$1     &   11400$\pm$83           &     -82$\pm$34       &    73.71$\pm$0.50    &     \\  
                                               &  54553     &   Ly$\alpha$   &   510.5              &    3207$^{(a)}$          &    ---                        &   ---                             &  SDSS DR12 SAS  \\
   \rowfont{\color{blue}}          & 54533      & \civ                & 284$\pm$13    & 4574$\pm$658         &   55$\pm$438.31     &  31.80$\pm$1.51         &     \\
   \rowfont{\color{blue}}          &  54533     &   \civ              &  ---                  &    4180$\pm$736     &    ---                        &    100.5$\pm$11.9       &  Shen2011   \\
   \rowfont{\color{blue}}          &  54553     &   \civ              & 462.6               &    4537$^{(a)}$           &    ---                       &   ---                              &  SDSS DR12 SAS  \\
                                                & 54533       & \ciii              & 105$\pm$7        &  3687$\pm$336       &  -246$\pm$122.7   &  33.29$\pm$2.32         &     \\
                                                &  54553      &  \ciii             &  164.6                &  4537$^{(a)}$             &  ---                         &  ---                           &   SDSS DR12 SAS \\  
    \rowfont{\color{teal}}           &   54533     & \mgii           &   ---                 &  4802$\pm$2005      &    ---                       &   115$\pm$33         &  Shen2011   \\
    \rowfont{\color{teal}}            &   54533    & \mgii           & 187.4                &  4537$^{(a)}$              &    ---                       &  ---                           &   SDSS DR12 SAS  \\
                                                 & 55832     & Ly$\alpha_{\rm na}$                  &   27$\pm$4              &  783$\pm$102        & -323$\pm$35            &    9.72$\pm$1.59       &     \\   
                                                 & 55832      & Ly$\alpha$    & 288$\pm$11   &  4444$\pm$243       &  -463$\pm$68         &  103.69$\pm$3.99     &     \\
                                              &   55832     & Ly$\alpha$    &   633.9            &    4165.6$^{(a)}$        &    ---                       &   ---                           &  SDSS DR12 SAS  \\
                & \textcolor{blue}{55832} & \textcolor{blue}{\civ}  &   \textcolor{blue}{73$\pm$3}               &  \textcolor{blue}{6253$\pm$259}   &  \textcolor{blue}{270$\pm$106}     &  \textcolor{blue}{45.15$\pm$1.90}      &     \\
    \rowfont{\color{blue}}           &   55832    &  \civ                &   -                     &    5210$\pm$226    &    ---                       &     42.76$\pm$1.96      &  Ham17  \\
    \rowfont{\color{blue}}           &   55832    &  \civ                &  125.1               &    5385$^{(a)}$          &    ---                       &   ---                             &  SDSS DR12 SAS  \\
                                                & 55832      & \ciii                 & 19$\pm$6         &  14952$\pm$4682  &    3000$\pm$0         &   17.79$\pm$5.49      &     \\
                                                 &  55832     &  \ciii                &  10.68               &     5385$^{(a)}$         &  ---                        &                                &  SDSS DR12 SAS\\  
    \rowfont{\color{teal}}           & 55832       & \mgii               &  41$\pm$7       &        0$\pm$0           &    1000$\pm$1108     &    81.76$\pm$13.90    &     \\
    \rowfont{\color{teal}}           &  55832      & \mgii               &  34.66               &     5385$^{(a)}$        &  ---                       &                                &  SDSS DR12 SAS\\  
      \rowfont{\color{blue}}        & 58583       & \civ                &  286$\pm$2         & -                                   &                   -                &   20.89$\pm$0.13      &     \\  
                                                & 58583       & \ciii                &   92$\pm$1          &  6689$\pm$89             &    37$\pm$37.186        &   28.96$\pm$0.35      &     \\  
    \rowfont{\color{teal}}          & 58583        & \mgii             &  116$\pm$1         &  6649$\pm$85             & -422$\pm$34.818       &   67.38$\pm$0.77      &     \\  
    \rowfont{\color{blue}}         &   56189      &   \civ            &   ---                       &   2994$\pm$620        &     ---                        &   42.18$\pm$5.59        &     Ham17  \\
    \rowfont{\color{blue}}          &   56189     &   \civ            &  48.67                     &    5218$^{(a)}$             &    ---                        &   ---                             &  SDSS DR12 SAS  \\
                                               & 56189        & \ciii               &  39$\pm$8            & 14097$\pm$2943      &   2243$\pm$1142    & 66.63$\pm$12.90         &     \\
                                                 &  56189     &   \ciii             &  17.2                      &     5218$^{(a)}$           &  ---                          &                                      &  SDSS DR12 SAS \\  
    \rowfont{\color{teal}}           & 56189       & \mgii            &  23$\pm$6             &   6694$\pm$1765      &   -597$\pm$741       & 41.19$\pm$10.95        &     \\
    \rowfont{\color{teal}}        &  56189         &   \mgii          &  33.6                      &     5218$^{(a)}$           &  ---                           &                                     &  SDSS DR12 SAS \\  
                                               & 56960       & Ly$\alpha_{\rm na}$   &   24$\pm$5    &     642$\pm$92         &    -319$\pm$30       &  2.71 $\pm$0.51          &     \\  
                                                & 56960      & Ly$\alpha$                & 121$\pm$38   & 3580$\pm$673         &     -16$\pm$171     &  13.52 $\pm$4.21        &     \\  
           & \textcolor{blue}{56960} & \textcolor{blue}{\civ}     & \textcolor{blue}{254$\pm$5}    &  \textcolor{blue}{8731$\pm$172}   &   \textcolor{blue}{92$\pm$68}  &   \textcolor{blue}{45.35$\pm$0.90}    &     \\   
                                               & 56960    & \ciii                   & 185$\pm$5              &        -                            &  2701$\pm$225       &   47.75$\pm$1.29      &     \\  
    \rowfont{\color{teal}}          & 56960    & \mgii                &   99$\pm$4              &  7312.6$\pm$340        &   188$\pm$137         &   50.75$\pm$2.21     &     \\
     \rowfont{\color{blue}}        & 58693    & \civ                   & 54.688$\pm$0.6    &  6000.3$\pm$70           &      33$\pm$28          &   39.28$\pm$0.43     &     \\  
                                               & 58693    & \ciii                   & 115.08$\pm$1.2    & 15000                            &  2772$\pm$86          &   96.36$\pm$0.97     &     \\  
     \rowfont{\color{teal}}         & 58693    & \mgii                & 46.361$\pm$1.3    & 8900$\pm$278             &  1000                         &   53.46$\pm$1.54     &     \\  
                                                %

@@

\caption{Line Measurement Information from QSFIT, unless otherwise stated. 

@@

      SDSS DR12 SAS is the line measurement information from the SDSS DR12

@@

>>>>

% \hypersetup{draft}

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

@@

\subsection{Line Properties}  
We use the measured quasar emission line properties from several catalogues: 
\citet{Shen2011}, \citet{Hamann2017}, \citet{Kozlowski2017} and
\citet{Calderone2017}.

\citet{Shen2011} present a compilation of properties of the 105,783
quasars in the SDSS Data Release 7 (DR7) quasar catalog \citep[DR7Q;
][]{Schneider2007}. \citet{Shen2011} report non-zero \civ\ FWHM and
EWs for approximately half (51,501) of the full DR7Q, and non-zero
\mgii FWHM and EWs for 80\% (84,183) of the DR7Q quasars).

\citet{Calderone2017} present the Quasar Spectral Fitting (QSFIT)
software package which among other quantities provides luminosity
estimates as well as width, velocity offset and equivalent width of 20
emission lines, includinng \civ, \ciii and \mgii.  We use the lastest
version (v1.3.0) of the QSFIT
\href{https://qsfit.inaf.it/cat_1.30/onlinefit.php}{online calculator}
and process our spectra with QSFit setting $E(B-V)=0.00$.

\citet{Hamann2017} in
particular investigate in robust detail the UV continuum and the \civ\
(and \nv $\lambda$ $\lambda$1238, 1242) emission lines in over 200,000
quasars in BOSS DR12Q \citep{Paris2017}\footnote{This emission-line
catalog can be downloaded from
\href{https://datadryad.org/stash/dataset/doi:10.6086/D1H59V}{here}.}
The quasar redshift are limited to the range $1.53 \leq z \leq 5.0$ so
that \civ\ and the adjacent continuum are covered by BOSS. These
measurements provide line profile information and flux ratios.
\citet{Hamann2017} was focused on $z\geq2$ quasars and specifcally
their \civ properties in order to understand the high-$z$ ``Extremely Red Quasar''
population \citet{Ross2015, Zakamska2016, Perrotta2019, Zakamska2019}. 
As such, these measurements can be taken as the
`gold standard' for \civ line measurement, though this is only for 2
out of our 9 spectra.

%% Notes.
 When using the \citet{Shen2011} catalogue, we report line luminosity,
FWHM, rest-frame equivalent width, and their errors for the {\it
whole} \mgii profile (the \citet{Shen2011} catalogue also quotes values
for just the broad \mgii compoment, but the differences here in the
two spectra of ours is negligible). The line luminosites in
\citet{Calderone2017} are given in units of $10^{42}$ erg s$^{-1}$,
while the line luminosites in \citet{Shen2011} are in units of
$\log(L)$.  So comparing the error values for these measurements is
not straightforward.

@@

  \begin{tabu}{lll  cccc c r }

@@

    Object                               &   MJD      & line      & Line  Lumin.       &  FWHM                      &  $V_{\rm off}$          & E.W.                          & $\alpha_{\lambda}$   &  Catalogue  \\                                   

@@

    \rowfont{\color{blue}}       & 53948    & \civ      &  523$\pm$14    &   9816$\pm$321       &  1407$\pm$81      &  16.83$\pm$0.43      & $-1.64\pm0.01$      & QSFit    \\
    \rowfont{\color{blue}}       & 53948    & \civ      &  787                   &   5230$\pm$219        &  1118$\pm$133    &    30.1$\pm$1.21      & $-1.47\pm0.08$      &  Shen2011  \\
    \rowfont{\color{blue}}       & 53948    & \civ      &                           &   5119$^{(a)}$             &    ---                     &   ---                          &  ---                           & DR12 SAS  \\
                                             & 53948     & \ciii      &  441$\pm$10   & 14959$\pm352^{(b)}$ &  2616$\pm$147    &  25.10$\pm$0.59      & $-1.65\pm0.01$      & QSFit   \\
                                             & 53948    & \ciii       &                          &   5119$^{(a)}$             &  ---                       &    ---                         &  ---                          & DR12 SAS \\
  \rowfont{\color{teal}}         & 53948     & \mgii     &  327$\pm$20   &   4907$\pm$387       &  $-274\pm419$     &  26.66$\pm$1.65     &   $-1.65\pm0.01$     &  QSFit  \\
  \rowfont{\color{teal}}         & 53948     & \mgii     &  284                  &   4730$\pm$314       &  $-179\pm188$     &  32$\pm$3.88           &  $-1.87\pm0.06$     & Shen2011 \\

@@

                &     \textcolor{teal}{53948}      & \textcolor{teal}{\mgii}   & \textcolor{teal}{---} & \textcolor{teal}{5119$^{(a)}$}   &  \textcolor{teal}{---}   & \textcolor{teal}{---}        & \textcolor{teal}{---}    & \textcolor{teal}{DR12 SAS}    \\
                \cdashline{2-9}
                                               & 58538     & \lya     & 1393$\pm$11   & $>$15000   &  $-796\pm57$      &  ---     &    &   QSFit  \\
    \rowfont{\color{blue}}        & 58538     & \civ      &  1037$\pm$5    & $>$15000   &  983$\pm$40        &  ---     &    &   QSFit    \\  
                                              & 58538      & \ciii     &    677$\pm$4    & $>$15000    & $>$3000              &  ---     &     &  QSFit   \\  
    \rowfont{\color{teal}}         & 58538     & \mgii    &     755$\pm$4  & $>$15000    & 350$\pm$39        &  ---      &    &   QSFit  \\
                                          \cdashline{2-9}
                                              & 58693      & \lya     & 290$\pm$3        & 8803$\pm$52      &  $-1096\pm35$  &  ---                        & $<$-3       &   QSFit  \\
    \rowfont{\color{blue}}        & 58693     & \civ      &   68$\pm$0.9     & 3743$\pm$26    &   591$\pm$17    &   ---                       & $<$-3     &  QSFit   \\  
                                              & 58693      & \ciii     &   19$\pm$0.4     & 5625$\pm$         &   $>$3000           &    ---                      & $<$-3    &  QSFit    \\  
    \rowfont{\color{teal}}         & 58693     & \mgii    &   19$\pm$0.4    & 1530$\pm$22     &  $>$3000          &    ---                          &$<$-3    &  QSFit   \\  
                                                & 54553     & \lya     &   510.5              &  3207          &    ---                        &   ---                             & ---   &   DR12 SAS  \\
   \rowfont{\color{blue}}          & 54533     & \civ      & 284$\pm$13    & 4574$\pm$658         &   55$\pm$438.31     &  31.80$\pm$1.51         &   &  QSFit  \\
   \rowfont{\color{blue}}          & 54533     & \civ      &  281                  &    4181$\pm$736     &    680$\pm$133       &    100.5$\pm$11.9       & $-0.14\pm0.68$  &  Shen2011   \\
   \rowfont{\color{blue}}          & 54553     & \civ      & 462.6                &    4537$^{(a)}$           &    ---                       &   ---                              & ---   &  DR12 SAS  \\
                                                & 54533     & \ciii     & 105$\pm$7       &  3687$\pm$336       &  $-246\pm122.7$   &  33.29$\pm$2.32         &    &  QSFit  \\
                                                & 54553     & \ciii     &  164.6                &  4537$^{(a)}$             &  ---                         &  ---                           & ---     &  DR12 SAS \\  
    \rowfont{\color{teal}}          & 54533      & \mgii  &   139                 &  4757$\pm$2224      &  $-944\pm568$        &   119$\pm$40         &  $-1.49\pm0.54$   &  Shen2011   \\
    \rowfont{\color{teal}}          & 54533      & \mgii  & 187.4                 &  4537$^{(a)}$              &    ---                       &  ---                           & ---    &  DR12 SAS  \\

@@

                                                & 55832     & \lya     & 288$\pm$11   &  4444$\pm$243       &  -463$\pm$68         &  103.69$\pm$3.99     &    &   QSFit  \\
                                                & 55832     & \lya     &   633.9            &    4165.6$^{(a)}$        &    ---                       &   ---                           &   ---   &   DR12 SAS  \\ 
                & \textcolor{blue}{55832} & \textcolor{blue}{\civ}  &   \textcolor{blue}{73$\pm$3}               &  \textcolor{blue}{6253$\pm$259}   &  \textcolor{blue}{270$\pm$106}     &  \textcolor{blue}{45.15$\pm$1.90}      &  &   QSFit    \\
    \rowfont{\color{blue}}           &  55832   &  \civ     &   -                     &    5210$\pm$226    &    ---                       &     42.76$\pm$1.96      &   &   Ham17  \\
    \rowfont{\color{blue}}           &  55832   &  \civ     &  125.1               &    5385$^{(a)}$          &    ---                       &   ---                             &   &   DR12 SAS  \\
                                                 & 55832     & \ciii     & 19$\pm$6         &  14952$\pm$4682  &    3000$\pm$0         &   17.79$\pm$5.49      &  &   QSFit    \\
                                                 &  55832    &  \ciii    &  10.68               &     5385$^{(a)}$         &  ---                        &                                &   &   DR12 SAS\\  
    \rowfont{\color{teal}}           & 55832      & \mgii   &  41$\pm$7       &        0$\pm$0           &    1000$\pm$1108     &    81.76$\pm$13.90    &    &   QSFit  \\
    \rowfont{\color{teal}}           &  55832     & \mgii   &  34.66               &     5385$^{(a)}$        &  ---                       &                                &   &   DR12 SAS\\  
                                               \cdashline{2-9}
      \rowfont{\color{blue}}        & 58583      & \civ      &  286$\pm$2     & -                                   &                   -                &   20.89$\pm$0.13      &   &   QSFit   \\  
                                                & 58583      & \ciii      &   92$\pm$1      &  6689$\pm$89             &    37$\pm$37.186        &   28.96$\pm$0.35      &   &   QSFit   \\  
    \rowfont{\color{teal}}           & 58583      & \mgii   &  116$\pm$1      &  6649$\pm$85             & -422$\pm$34.818       &   67.38$\pm$0.77      &   &   QSFit   \\  
    \rowfont{\color{blue}}         &   56189      & \civ    &   ---                       &   ---                          &     ---                        &    ---                             &     &   QSFit$^{(c)}$  \\
    \rowfont{\color{blue}}         &   56189      & \civ    &   ---                       &   2994$\pm$620        &     ---                        &   42.18$\pm$5.59        &    &    Ham17  \\
    \rowfont{\color{blue}}         &   56189      & \civ    &  48.67                     &    5218$^{(a)}$             &    ---                        &   ---                             &   &   DR12 SAS  \\
                                               & 56189        &  \ciii   &  39$\pm$8            & 14097$\pm$2943      &   2243$\pm$1142    & 66.63$\pm$12.90         &    &   QSFit  \\
                                               &  56189       & \ciii    &  17.2                      &     5218$^{(a)}$           &  ---                          &                                      &   &   DR12 SAS \\  
    \rowfont{\color{teal}}          & 56189       & \mgii  &  23$\pm$6             &   6694$\pm$1765      &   -597$\pm$741       & 41.19$\pm$10.95        &  &   QSFit   \\
    \rowfont{\color{teal}}         &  56189       &  \mgii &  33.6                      &     5218$^{(a)}$           &  ---                           &                                     &   &   DR12 SAS \\  
                                                  \cdashline{2-9}
                                              & 56960         & \lya    & 121$\pm$38   & 3580$\pm$673         &     -16$\pm$171     &  13.52 $\pm$4.21        &  &   QSFit   \\  
           & \textcolor{blue}{56960} & \textcolor{blue}{\civ}     & \textcolor{blue}{254$\pm$5}    &  \textcolor{blue}{8731$\pm$172}   &   \textcolor{blue}{92$\pm$68}  &   \textcolor{blue}{45.35$\pm$0.90}    &    &    \\   
                                               & 56960    & \ciii        & 185$\pm$5              &        -                            &  2701$\pm$225       &   47.75$\pm$1.29      &  &   QSFit    \\  
   \rowfont{\color{teal}}           & 56960    & \mgii     &   99$\pm$4              &  7312.6$\pm$340        &   188$\pm$137         &   50.75$\pm$2.21     &   &   QSFit   \\

@@

     \rowfont{\color{blue}}        & 58693    & \civ      & 54.688$\pm$0.6    &  6000.3$\pm$70           &      33$\pm$28          &   39.28$\pm$0.43     &   &   QSFit   \\  
                                               & 58693    & \ciii       & 115.08$\pm$1.2    & 15000                            &  2772$\pm$86          &   96.36$\pm$0.97     &   &   QSFit   \\  
     \rowfont{\color{teal}}         & 58693    & \mgii    & 46.361$\pm$1.3    & 8900$\pm$278             &  1000                         &   53.46$\pm$1.54     &   &   QSFit   \\  

@@

\caption{Line Measurement Information from   %\href{QSFIT}{https://qsfit.inaf.it/}, unless otherwise stated. 

@@

      DR12 SAS is the line measurement information from the SDSS DR12 

@@

      Positive values of Voff means the line is blueshifted.
      $^{(b)}$Bit 3: FWHM value hits a limit in the fit;
      $^{(c)}$QSFit does not fit the \civ line. 
